Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-21 paper/main.tex
composition outline + notes

\subsection{Artist Composition}
\label{sec:artist:union}
\begin{figure}[!h]
\centering
\subfloat[+]{\includegraphics[width=.4\columnwidth]{exploding_artist.png}%
\label{fig:artist:union:glue}}
%\hfil
\subfloat[$\oplus$]{\includegraphics[width=.4\columnwidth]{combined_artist.png}%
\label{fig:artist:union:continuity}}
\caption{In \autoref{fig:artist:union:glue}, the outputs of various artist are independently rendered to the same graphic space \gtotal. The inputs to the artists in \autoref{fig:artist:union:continuity} are sections over the same fiber bundle base space \dbase; therefore, they should share transformation functions to produce a consistent image. \note{add a border/make the same size/etc so 1 doesn't run over into two}}
\end{figure}
%% artist composition is fiber products/sums of artists on sheafs -> closed cartesian category maybe?

Visualizations generally consist of more than one graphic, for example two line plots, a legend, axis ticks, spines, and labels. \note{formalize superposition, than break down what that means for composition}
\subsubsection{Superposition: union}

These graphics can be generated by disjoint data inputs  $(\dtotal_i: i\in I)$ into different artist functions $\vartist$ with the same output target space $\gtotal$. We define this composition via the disjoint union of the inputs 
\begin{equation}
  \label{eq:artist:union:glue}
+ \coloneqq \underset{i\in I}{\sqcup} \dtotal_{i}
\end{equation}
This approach does not guarantee a coherent image, as illustrated in \autoref{fig:artist:union:glue}, because each data is explicitly considered as distinct from the others.

\subsection{Shared properties: intersection}
Many times though, graphics are generated from subsets of a larger data set, such as when using multiple views \cite{alboRadarComparativeEvaluation2016a, hullmanKeeping2018} and brush-linked views \cite{beckerBrushingScatterplots1987,bujaInteractiveData1991}. In these situations, we consider each of the data inputs as component bundles over a shared continuity \dbase.

\begin{equation}
  \label{eq:math:data:base:decompose}
  \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}

The sections $\dsection$ on each component bundle $\dtotal_i$ over a point $\dbasepoint \in \dbase$ are the elements of the data associated with that point. We use this property to establish which of these elements are the same, because they come from the same fiber, and therefore should share transformation functions to visual elements. This bookkeeping yields graphics with consistent visual encoding of data elements, as shown in \autoref{fig:artist:union:continuity}.

>>>>

\subsection{Multiple Graphics: Superposition and Composition}
\label{sec:artist:union}
\begin{figure}[!h]
\centering
\subfloat[+]{\includegraphics[width=.4\columnwidth]{exploding_artist.png}%
\label{fig:artist:union:glue}}
%\hfil
\subfloat[$\oplus$]{\includegraphics[width=.4\columnwidth]{combined_artist.png}%
\label{fig:artist:union:continuity}}
\caption{In \autoref{fig:artist:union:glue}, the outputs of various artist are independently rendered to the same graphic space \gtotal. The inputs to the artists in \autoref{fig:artist:union:continuity} are sections over the same fiber bundle base space \dbase; therefore, they should share transformation functions to produce a consistent image. \note{add a border/make the same size/etc so 1 doesn't run over into two}}
\end{figure}
%% artist composition is fiber products/sums of artists on sheafs -> closed cartesian category maybe?

Visualizations generally consist of more than one graphic, for example two line plots, a legend, axis ticks, spines, and labels. \note{formalize superposition, than break down what that means for composition}
\subsubsection{Superposition: Multiple Datasets}
\note{far as we care, this can technically be A = A1 + A2....}

\subsubsection{Composite Artist: Multivariate Datasets}
\note{This is A = A_1 \circ A_2 b\c it's sharing nus or xis or all of the above}

\paragraph{Overlapping Base Spaces}

\paragraph{Shared Fibers}
